MCREX: Using Monte Carlo Algorithms to Achieve Resiliency \& Performance at Scale for Linear and Nonlinear Solver Applications

### 2016-01-28 doc/ecp/pres.tex
Final presentation.

\logo{\includegraphics[width=2cm]{new_logo}}

\setbeamercolor{item}{fg=MSUgreen}
\beamertemplatenavigationsymbolsempty
\setbeamertemplate{headline}{}
\setbeamertemplate{footline}{
  \insertframenumber/\inserttotalframenumber}
\setbeamertemplate{title page}
{
  \begin{tabular}{cr}
    \begin{minipage}{5.5cm}
      {\RaggedRight \bf \large \textcolor{MSUgreen}{\inserttitle}}\\
      \vspace{\baselineskip}\\
      \insertauthor\\
      \vspace{0.5\baselineskip}\\
      \insertinstitute\\
      \insertdate
    \end{minipage}
  \end{tabular}
}

@@

\title[MCREX]{Using Monte Carlo Algorithms to Achieve Resiliency \& Performance
  at Scale for Linear and Nonlinear Solver Applications}
\author{Thomas Evans (PI, ORNL)\\
  Michele Benzi (Co-PI, Emory)\\
  Steven Hamilton (ORNL)\\
  Stuart Slattery (ORNL)\\
  Christian Engelmann (ORNL)\\
  Wayne Joubert (ORNL)\\
  Massimiliano Lupo Pasini (Emory)
}
\date[DOE, 2016]{DOE RX-Solvers, 1/29/2016}
%\institute[ORNL]{Oak Ridge National Lab}

@@

{
  \usebackgroundtemplate{
    \includegraphics[width=\paperwidth,height=\paperheight]{title_template}}
  \setbeamertemplate{logo}{}
  \begin{frame}
    \titlepage
  \end{frame}
}

@@

  We have also developed scalable parallel algorithms that can take advantage
  of the benefits of replicating Monte Carlo random walks
  \begin{itemize}
  \item Developed multilevel parallel strategies for domain decomposed Monte
    Carlo that allows redundancy
  \item Developed concurrent on-node random walk algorithms for GPU
    optimization
  \end{itemize}

@@

  First reference, G.E. Forsythe and R.A. Leibler. Matrix Inverstion by a
  Monte Carlo Method. \textit{Math. Tables and Comp.}, {\bf 4}(31), 127--129,
  1950 (credited to von Neumann and Ulam, 1940s).
  \vfill
  \begin{itemize}
    \item Suppose we want to solve $\mathbf{Ax}=\mathbf{b}$
    \vfill
    \item If $\rho(\mathbf{I-A})<1$, we can write the solution using the
      Neumann series
      \begin{equation*}
        \mathbf{x} = \sum_{n=0}^{\infty} (\mathbf{I-A})^n \mathbf{b}
         = \sum_{n=0}^{\infty} \mathbf{H}^n \mathbf{b}
      \end{equation*}
      where $\mathbf{H} \equiv ( \mathbf{I-A} )$ is the Richardson
      iteration matrix
      \vfill
    \item Build the Neumann series stochastically
  \end{itemize}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics<1>[width=4in]{../NCState_seminar_2014/adjoint_1}
      \includegraphics<2>[width=4in]{../NCState_seminar_2014/adjoint_10}
      \includegraphics<3>[width=4in]{../NCState_seminar_2014/adjoint_100}
      \includegraphics<4>[width=4in]{../NCState_seminar_2014/adjoint_1000}
      \includegraphics<5>[width=4in]{../NCState_seminar_2014/adjoint_10000}
      \includegraphics<6>[width=4in]{../NCState_seminar_2014/adjoint_100000}
      \includegraphics<7>[width=4in]{../NCState_seminar_2014/adjoint_1000000}
      \includegraphics<8>[width=4in]{../NCState_seminar_2014/adjoint_10000000}
    \end{center}
    \caption{
      \only<1>{\textbf{Adjoint solution.}
        \textit{\sn{1}{0} total histories.} }
      \only<2>{\textbf{Adjoint solution.}
        \textit{\sn{1}{1} total histories.} }
      \only<3>{\textbf{Adjoint solution.}
        \textit{\sn{1}{2} total histories.} }
      \only<4>{\textbf{Adjoint solution.}
        \textit{\sn{1}{3} total histories.} }
      \only<5>{\textbf{Adjoint solution.}
        \textit{\sn{1}{4} total histories.} }
      \only<6>{\textbf{Adjoint solution.}
        \textit{\sn{1}{5} total histories.} }
      \only<7>{\textbf{Adjoint solution.}
        \textit{\sn{1}{6} total histories.} }
      \only<8>{\textbf{Adjoint solution.}
        \textit{\sn{1}{7} total histories.} }
    }
  \end{figure}
\end{frame}

@@

\begin{frame}{Why limit to the Neumann series polynomial?}
  \begin{itemize}
  \item Chebyshev or GMRES polynomials are viable alternatives
  \vfill
  \item A good approximation to a few terms in the polynomial
    performs better than a statistically noisy approximation to
    full series
  \vfill
  \item Using history length cutoff rather than weight cutoff can lead to
    large reductions in iteration counts
  \vfill
  \item Significant reduction in iteration counts are possible using
    alternate polynomials, but partially offset by increase in number
    of histories required
  \end{itemize}
  \vfill

  \begin{table}
    \caption{Polynomial MCSA - Shifted Laplacian}
    \centering
    \begin{tabular}{cccc}
      \toprule
      Polynomial & Polynomial & MCSA & Histories per \\
      Type & Order & Iterations & Iteration \\
      \midrule
      Neumann & 4 & 502 & 500 \\
      Chebyshev & 4 & 246 & 16000 \\
      GMRES & 4 & 260 & 2000 \\
      \bottomrule
    \end{tabular}
  \end{table}

@@

  \begin{table}
  \centering
  \begin{tabular}{cccc}
  \toprule
  \textbf{Block size} & \textbf{$\frac{nnz(H)}{nnz(A)}$}& $\rho(H)$
  &$\rho(\hat{H})$\\
  \midrule
   3 & 1.4352 & $0.9804$ & $0.9531$\\
   9 & 3.0220 & $0.9790$ & $0.9674$\\
   33 & 9.8164 & $0.9783$  & $0.9774$\\
  \bottomrule
  \end{tabular}
  \caption{$\rho(H)$ and $\rho(\hat{H})$ for advection--diffusion
  matrix with block diagonal preconditioning.}
  \label{tab:ifiss_block}
  \end{table}
\end{frame}

@@

  \begin{table}
  \centering
  \begin{tabular}{cccc}
  \toprule
  \textbf{Drop tolerance} & \textbf{$\frac{nnz(H)}{nnz(A)}$}& $\rho(H)$
  &$\rho(\hat{H})$\\
  \midrule
   0.05 & 8.2797 & $0.9610$ & $1.0231$  \\
   0.01 & 33.1390 & $0.8668$ & $0.8279$ \\
  \bottomrule
  \end{tabular}
  \caption{$\rho(H)$ and $\rho(\hat{H})$ for 2D
  Laplacian with AINV preconditioning.}
  \label{tab:lap2d_ainv}
  \end{table}
\end{frame}

@@

  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        \setlength{\itemsep}{-0.4\baselineskip}
      \item Each parallel process owns a piece of the domain (linear
        system)
        \bigskip
      \item Random walks must be transported between adjacent domains
        through parallel communication
        \bigskip
      \item Domain decomposition determined by the input system
        \bigskip
      \item Load balancing not yet addressed
        \bigskip
      \item Uses modified version of the Milagro algorithm (LANL)
      \end{itemize}
    \end{column}

@@

\begin{frame}{Publications and Presentations}

  \underline{Publications}
  \begin{itemize}
  \item M. Benzi, T.M. Evans, S.P. Hamilton, M.L. Pasini, and
    S.R. Slattery. Analysis of Monte Carlo Accelerated Iterative Methods for
    Sparse Linear Systems. \textit{in preparation}, 2016.
  \item S.R. Slattery, T.M. Evans, P.P.H. Wilson. A Spectral Analysis of the
    Domain Decomposed Monte Carlo Method for Linear Systems. \textit{Nuclear
      Engineering Design},  {\bf 295}, 632--638, 2015.
  \item T.M. Evans, S.W. Mosher, S.R. Slattery, and S.P. Hamilton. A Monte Carlo
    Synthetic Acceleration Method for Solving the Thermal Radiation Diffusion
    Equation. \textit{J. Comp. Phys.}, {\bf 258}, 338--358, 2014.
  \end{itemize}

@@

\begin{frame}{Publications and Presentations}

  \underline{Presentations}
  \begin{itemize}
    \footnotesize
    \setlength{\itemsep}{-0.1\baselineskip}
  \item Monte Carlo Synthetic Acceleration Methods for Sparse Linear Systems
    (M.L. Pasini, M. Benzi, T. Evans, S. Hamilton, S. Slattery), \textit{SIAM
      ALA}, October 30, 2015.
  \item Parallel Algorithms for the Monte Carlo Synthetic Acceleration Linear
    Solver Method (S. Slattery, T. Evans, S. Hamilton), \textit{SIAM CSE},
    Salt Lake City, 2015.
  \item Iterative Performance of Monte Carlo Linear Solver Methods
    (M.L. Pasini), \textit{SIAM CSE}, Salt Lake City, 2015.
  \item A multilevel Monte Carlo method for linear systems (S. Slattery,
    T. Evans, S. Hamilton), \textit{Copper Mountain Conference on Iterative
      Solvers}, Copper MT, CO, 2014.
  \item Monte Carlo Synthetic Acceleration as approximate polynomial
    preconditioning (S. Hamilton, T. Evans, S. Slattery), \textit{Copper
      Mountain Conference on Iterative Solvers}, Copper MT, CO, 2014.
  \item Monte Carlo Linear Solvers (S. Slattery, T. Evans, S. Hamilton),
    \textit{NC State Seminar}, Nov. 4, 2014.
  \item Monte Carlo Linear Solvers (S. Hamilton, T. Evans, S. Slattery),
    \textit{Emory Mathematics Dept. Seminar}, Sept. 19, 2014.
  \item Monte Carlo Methods for Linear Systems (T. Evans), \textit{MIT Nuclear
      Engineering Dept Seminar Series}, Sept. 30, 2014.
  \end{itemize}

@@

      \small{
        \begin{table}
          \begin{center}
            \begin{tabular}{lccc}
              \toprule
              \multicolumn{1}{l}{Benchmark}&
              \multicolumn{1}{c}{NK}&
              \multicolumn{1}{c}{FANM}&
              \multicolumn{1}{c}{NR}\\
              \midrule
              Ra=\sn{1}{3} & 5 & 5 & 5\\
              Ra=\sn{1}{4} & 7 & 7 & 7\\
              Ra=\sn{1}{5} & 9 & 10 & 9\\
              Ra=\sn{1}{6} & 11 & 11 & 11\\
              %%
              \bottomrule
            \end{tabular}`
          \end{center}
          \caption{Nonlinear iterations.}
        \end{table}

        \begin{table}
          \begin{center}
            \begin{tabular}{lccc}
              \toprule
              \multicolumn{1}{l}{Benchmark}&
              \multicolumn{1}{c}{GMRES}&
              \multicolumn{1}{c}{MCSA}&
              \multicolumn{1}{c}{Richardson}\\
              \midrule
              Ra=\sn{1}{3} & 32 & 18 & 38\\
              Ra=\sn{1}{4} & 23 & 17 & 34\\
              Ra=\sn{1}{5} & 25 & 20 & 34\\
              Ra=\sn{1}{6} & 39 & 25 & 48\\
              %%
              \bottomrule
            \end{tabular}
          \end{center}
          \caption{Total linear solver iterations.}
        \end{table}
      }

@@

  \begin{itemize}
  \item Use xSIM to model communication performance of MPI messaging
    \begin{itemize}
    \item Latency, bandwidth, contention, routing, and rendevous protocol
    \item Star, ring, mesh, torus, twisted torus, and tree topologies
    \item Hierarchical combinations of topologies, e.g. on-chip, on-node,
      off-node
    \end{itemize}
  \item Also used to simulate hard errors to test for detection and recovery
  \end{itemize}
  \vfill
  \begin{figure}
    \centering
    \includegraphics[height=.4\textwidth]{xsim}
  \end{figure}

>>>>

\logo{\includegraphics[width=2cm]{faded_logo}}

\setbeamercolor{item}{fg=MSUgreen}
\beamertemplatenavigationsymbolsempty
%\setbeamertemplate{headline}{}
%\setbeamertemplate{footline}{
%  \insertframenumber/\inserttotalframenumber}

\setbeamertemplate{title page}
{
  \begin{tabular}{cr}
    \begin{minipage}{5.5cm}
      {\RaggedRight \bf \large \textcolor{MSUgreen}{\inserttitle}}\\
      \vspace{\baselineskip}\\
      \insertauthor\\
      %\vspace{0.5\baselineskip}\\
      \insertinstitute\\
      \insertdate
    \end{minipage}
  \end{tabular}
}

@@

\title[MCREX]{MCREX: Using Monte Carlo Algorithms to Achieve Resiliency \&
  Performance at Scale for Linear and Nonlinear Solver Applications}
\author[Evans et al.]{Thomas Evans (PI, ORNL)\\
  Michele Benzi (Co-PI, Emory)\\
  Steven Hamilton (ORNL)\\
  Stuart Slattery (ORNL)\\
  Christian Engelmann (ORNL)\\
  Wayne Joubert (ORNL)\\
  Massimiliano Lupo Pasini (Emory) }
\date[DOE, 2016]{DOE RX-Solvers, 1/29/2016}
%\institute[ORNL]{Oak Ridge National Lab}

@@

{
  \setbeamertemplate{headline}{}
  \setbeamertemplate{footline}{}
  \usebackgroundtemplate{
    \includegraphics[width=\paperwidth,height=\paperheight]{title_template}}
  \setbeamertemplate{logo}{}
  \begin{frame}[plain]
    \titlepage
  \end{frame}
}

@@

  We have also developed scalable parallel algorithms that can take advantage
  of the benefits of replicating Monte Carlo random walks
  \begin{itemize}
  \item Developed multilevel parallel strategies for domain decomposed Monte
    Carlo that allows redundancy
  \item Developed on-node random walk algorithms for GPU optimization
  \end{itemize}

@@

  First reference: G.E. Forsythe and R.A. Leibler. Matrix Inversion by
    a Monte Carlo Method. \textit{Math. Tables and Comp.}, {\bf 4}(31),
    127--129, 1950 (credited to von Neumann and Ulam, 1940s).
  \begin{itemize}
    \item Suppose we want to solve $\mathbf{Ax}=\mathbf{b}$
    \vfill
    \item If $\rho(\mathbf{I-A})<1$, we can write the solution using the
      Neumann series
      \begin{equation*}
        \mathbf{x} = \sum_{n=0}^{\infty} (\mathbf{I-A})^n \mathbf{b}
         = \sum_{n=0}^{\infty} \mathbf{H}^n \mathbf{b}
      \end{equation*}
      where $\mathbf{H} \equiv ( \mathbf{I-A} )$ is the Richardson
      iteration matrix
      \vfill
    \item Build the Neumann series stochastically
  \end{itemize}

@@

  \begin{figure}[h!]
    \begin{center}
      \includegraphics<1>[width=4in]{../NCState_seminar_2014/adjoint_1}
      \includegraphics<2>[width=4in]{../NCState_seminar_2014/adjoint_10}
      \includegraphics<3>[width=4in]{../NCState_seminar_2014/adjoint_100}
      \includegraphics<4>[width=4in]{../NCState_seminar_2014/adjoint_1000}
      \includegraphics<5>[width=4in]{../NCState_seminar_2014/adjoint_10000}
      \includegraphics<6>[width=4in]{../NCState_seminar_2014/adjoint_100000}
      \includegraphics<7>[width=4in]{../NCState_seminar_2014/adjoint_1000000}
      \includegraphics<8>[width=4in]{../NCState_seminar_2014/adjoint_10000000}
    \end{center}
    \caption{
      \only<1>{\textit{\sn{1}{0} total histories.} }%
      \only<2>{\textit{\sn{1}{1} total histories.} }%
      \only<3>{\textit{\sn{1}{2} total histories.} }%
      \only<4>{\textit{\sn{1}{3} total histories.} }%
      \only<5>{\textit{\sn{1}{4} total histories.} }%
      \only<6>{\textit{\sn{1}{5} total histories.} }%
      \only<7>{\textit{\sn{1}{6} total histories.} }%
      \only<8>{\textit{\sn{1}{7} total histories.} }%
    }
  \end{figure}
\end{frame}

@@

\begin{frame}{Why limit to the Neumann series polynomial?}
  \begin{itemize}
  \item Chebyshev or GMRES polynomials are viable alternatives
  \vfill
  \item A good approximation to a few terms in the polynomial
    performs better than a statistically noisy approximation to
    full series
  \vfill
  \item Using history length cutoff rather than weight cutoff can lead to
    large reductions in iteration counts
  \vfill
  \item Significant reduction in iteration counts are possible using
    alternate polynomials, but partially offset by increase in number
    of histories required
  \end{itemize}
  \vspace{-0.6\baselineskip}
  \begin{table}
    \caption{Polynomial MCSA - Shifted Laplacian}
    \centering
    \begin{tabular}{cccc}
      \toprule
      Polynomial & Polynomial & MCSA & Histories per \\
      Type & Order & Iterations & Iteration \\
      \midrule
      Neumann & 4 & 502 & 500 \\
      Chebyshev & 4 & 246 & 16000 \\
      GMRES & 4 & 260 & 2000 \\
      \bottomrule
    \end{tabular}
  \end{table}

@@

  \begin{table}
  \centering
  \caption{Advection--diffusion matrix with block diagonal preconditioning.}
  \begin{tabular}{cccc}
  \toprule
  \textbf{Block size} & \textbf{$\frac{nnz(H)}{nnz(A)}$}& $\rho(H)$
  &$\rho(\hat{H})$\\
  \midrule
   3 & 1.4352 & $0.9804$ & $0.9531$\\
   9 & 3.0220 & $0.9790$ & $0.9674$\\
   33 & 9.8164 & $0.9783$  & $0.9774$\\
  \bottomrule
  \end{tabular}
  \end{table}
\end{frame}

@@

  \begin{table}
  \centering
  \caption{2D Laplacian with AINV preconditioning.}
  \begin{tabular}{cccc}
  \toprule
  \textbf{Drop tolerance} & \textbf{$\frac{nnz(H)}{nnz(A)}$}& $\rho(H)$
  &$\rho(\hat{H})$\\
  \midrule
   0.05 & 8.2797 & $0.9610$ & $1.0231$  \\
   0.01 & 33.1390 & $0.8668$ & $0.8279$ \\
  \bottomrule
  \end{tabular}
  \end{table}
\end{frame}

@@

  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
        %\setlength{\itemsep}{-0.4\baselineskip}
      \item Each parallel process owns a piece of the domain (linear
        system)
      \item Random walks must be transported between adjacent domains
        through parallel communication
      \item Domain decomposition determined by the input system
      \item Load balancing not yet addressed
      \item Uses modified version of the Milagro algorithm (LANL)
      \end{itemize}
    \end{column}

@@

\begin{frame}{Publications}

  \begin{itemize}
  \item M. Benzi, T.M. Evans, S.P. Hamilton, M.L. Pasini, and
    S.R. Slattery. Analysis of Monte Carlo Accelerated Iterative Methods for
    Sparse Linear Systems. \textit{in preparation}, 2016.
  \item C. Engelmann and T. Naughton. A New Deadlock Resolution Protocol and
    Message Matching Algorithm for the Extreme-scale
    Simulator. \textit{Concurrency and Computation: Practice and Experience,
      2016}. John Wiley \& Sons, Inc.. ISSN 1532-0634, 2016.
  \item S.R. Slattery, T.M. Evans, P.P.H. Wilson. A Spectral Analysis of the
    Domain Decomposed Monte Carlo Method for Linear Systems. \textit{Nuclear
      Engineering Design},  {\bf 295}, 632--638, 2015.
  \item T.M. Evans, S.W. Mosher, S.R. Slattery, and S.P. Hamilton. A Monte Carlo
    Synthetic Acceleration Method for Solving the Thermal Radiation Diffusion
    Equation. \textit{J. Comp. Phys.}, {\bf 258}, 338--358, 2014.
  \end{itemize}

@@

\begin{frame}{Conferences}

  \begin{itemize}
    \footnotesize
    \setlength{\itemsep}{-0.1\baselineskip}
  \item C. Engelmann and T. Naughton. Supporting the Development of Soft-Error
    Resilient Message Passing Applications using Simulation. In
    \textit{Proceedings of the 13th IASTED International Conference on
      Parallel and Distributed Computing and Networks (PDCN) 2016}, Innsbruck,
    Austria, February 15-16, 2016. ACTA Press, Calgary, AB, Canada.
  \item Monte Carlo Synthetic Acceleration Methods for Sparse Linear Systems
    (M.L. Pasini, M. Benzi, T. Evans, S. Hamilton, S. Slattery), \textit{SIAM
      ALA}, October 30, 2015.
  \item Parallel Algorithms for the Monte Carlo Synthetic Acceleration Linear
    Solver Method (S. Slattery, T. Evans, S. Hamilton), \textit{SIAM CSE},
    Salt Lake City, 2015.
  \item C. Engelmann and T. Naughton. A Network Contention Model for the
    Extreme-scale Simulator. In \textit{Proceedings of the 34th IASTED
      International Conference on Modelling, Identification and Control (MIC)
      2015}, Innsbruck, Austria, February 17-18, 2015. ACTA Press, Calgary,
    AB, Canada.
  \item Iterative Performance of Monte Carlo Linear Solver Methods
    (M.L. Pasini), \textit{SIAM CSE}, Salt Lake City, 2015.
  \end{itemize}

\begin{frame}{Conferences}

  \begin{itemize}
    \footnotesize
    \setlength{\itemsep}{-0.1\baselineskip}
  \item A multilevel Monte Carlo method for linear systems (S. Slattery,
    T. Evans, S. Hamilton), \textit{Copper Mountain Conference on Iterative
      Solvers}, Copper MT, CO, 2014.
  \item Monte Carlo Synthetic Acceleration as approximate polynomial
    preconditioning (S. Hamilton, T. Evans, S. Slattery), \textit{Copper
      Mountain Conference on Iterative Solvers}, Copper MT, CO, 2014.
  \item C. Engelmann and T. Naughton. Improving the Performance of the
    Extreme-scale Simulator. In \textit{Proceedings of the 18th IEEE/ACM
      International Symposium on Distributed Simulation and Real Time
      Applications (DS-RT) 2014}, pages 198-207, Toulouse, France, October
    1-3, 2014. IEEE Computer Society, Los Alamitos, CA, USA. ISBN
    978-1-4799-6143-6. ISSN 1550-6525.
  \item T. Naughton, C. Engelmann, G. Vallée, and S. Böhm. Supporting the
    Development of Resilient Message Passing Applications using Simulation. In
    \textit{Proceedings of the 22nd Euromicro International Conference on
      Parallel, Distributed, and network-based Processing (PDP) 2014}, pages
    271-278, Turin, Italy, February 12-14, 2014. IEEE Computer Society, Los
    Alamitos, CA, USA. ISSN 1066-6192. Acceptance rate 32.6\% (73/224).
  \end{itemize}

\begin{frame}{Presentations}

  \begin{itemize}
  \item Monte Carlo Linear Solvers (S. Slattery, T. Evans, S. Hamilton),
    \textit{NC State Seminar}, Nov. 4, 2014.
  \item Monte Carlo Linear Solvers (S. Hamilton, T. Evans, S. Slattery),
    \textit{Emory Mathematics Dept. Seminar}, Sept. 19, 2014.
  \item Monte Carlo Methods for Linear Systems (T. Evans), \textit{MIT Nuclear
      Engineering Dept Seminar Series}, Sept. 30, 2014.
  \end{itemize}

@@

      \small{
        \begin{table}
          \begin{center}
            \begin{tabular}{lccc}
              \toprule
              \multicolumn{1}{l}{Benchmark}&
              \multicolumn{1}{c}{NK}&
              \multicolumn{1}{c}{FANM}&
              \multicolumn{1}{c}{NR}\\
              \midrule
              Ra=\sn{1}{3} & 5 & 5 & 5\\
              Ra=\sn{1}{4} & 7 & 7 & 7\\
              Ra=\sn{1}{5} & 9 & 10 & 9\\
              Ra=\sn{1}{6} & 11 & 11 & 11\\
              %%
              \bottomrule
            \end{tabular}`
          \end{center}
          \caption{Nonlinear iterations.}
        \end{table}
        \vspace{-0.5\baselineskip}
        \begin{table}
          \begin{center}
            \begin{tabular}{lccc}
              \toprule
              \multicolumn{1}{l}{Benchmark}&
              \multicolumn{1}{c}{GMRES}&
              \multicolumn{1}{c}{MCSA}&
              \multicolumn{1}{c}{Richardson}\\
              \midrule
              Ra=\sn{1}{3} & 32 & 18 & 38\\
              Ra=\sn{1}{4} & 23 & 17 & 34\\
              Ra=\sn{1}{5} & 25 & 20 & 34\\
              Ra=\sn{1}{6} & 39 & 25 & 48\\
              %%
              \bottomrule
            \end{tabular}
          \end{center}
          \caption{Total linear solver iterations.}
        \end{table}
      }

@@

  \begin{itemize}
  \item Use xSIM to model communication performance of MPI messaging
    \begin{itemize}
    \item Latency, bandwidth, contention, routing, and rendevous protocol
    \item Star, ring, mesh, torus, twisted torus, and tree topologies
    \item Hierarchical combinations of topologies, e.g. on-chip, on-node,
      off-node
    \end{itemize}
  \item Also used to simulate hard errors to test for detection and recovery
  \end{itemize}
  \vfill
  \begin{figure}
    \centering
    \includegraphics[height=.35\textwidth]{xsim}
  \end{figure}
